---
title: "dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

```{r, message=FALSE, results='hide'}
data("instacart") 
janitor::clean_names(instacart)
```

Column {data-width=450}
-----------------------------------------------------------------------

###  Total number of items (< 500) ordered in each aisle

```{r, warning=FALSE, message=FALSE}
instacart1=
instacart %>%
  count(aisle) %>% 
  filter(n < 500) %>% 
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  plot_ly(
    x = ~aisle, y = ~n, type = "scatter", mode = "markers",
    color = ~aisle, alpha = 0.8) %>% 
  layout(title = "Total number of items (< 500) ordered in each aisle")
instacart1
```

Column {data-width=450}
-----------------------------------------------------------------------

### Total number of items (< 100000) ordered in each department 

```{r}
instacart2=
instacart %>%
  count(department) %>% 
  filter(n < 100000) %>% 
  mutate(department = fct_reorder(department, n)) %>% 
  plot_ly(
    x = ~department, y = ~n, color = ~department, type = "bar", colors = "viridis") %>% 
  layout(title = "Total number of items (< 100000) ordered in each department")
instacart2
```

### Mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered 

```{r, message=FALSE}
instacart3=
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarize(mean_hour = mean(order_hour_of_day)) %>%
  plot_ly(y = ~mean_hour, color = ~product_name, type = "box", colors = "viridis") %>% 
  layout(title = "Mean hour at which Pink Lady Apples and Coffee Ice Cream are ordered")
instacart3
```

