---
title: "dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```
After loading libraries, I used "Instacart" dataset to create a scatter plot, a bar chart and a box plot. 

```{r, message=FALSE, results='hide'}
data("instacart") 
janitor::clean_names(instacart)
```

Column {data-width=650}
-----------------------------------------------------------------------

###  Total number of items (< 500) ordered in each aisle

```{r, warning=FALSE, message=FALSE}
instacart1=
instacart %>%
  count(aisle) %>% 
  filter(n < 500) %>% 
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  plot_ly(
    x = ~aisle, y = ~n, type = "scatter", mode = "markers",
    color = ~aisle, alpha = 0.8) %>% 
  layout(title = "Total number of items (< 500) ordered in each aisle")
instacart1
```

Column {data-width=350}
-----------------------------------------------------------------------

### Total number of items (< 100000) ordered in each department 

```{r}
instacart2=
instacart %>%
  count(department) %>% 
  filter(n < 100000) %>% 
  mutate(department = fct_reorder(department, n)) %>% 
  plot_ly(
    x = ~department, y = ~n, color = ~department, type = "bar", colors = "viridis") %>% 
  layout(title = "Total number of items (< 100000) ordered in each department")
instacart2
```

### Order (<35) in which each product was added to cart in each department 

```{r}
instacart3=
instacart %>%
  filter(add_to_cart_order < 35) %>% 
  mutate(department = fct_reorder(department, add_to_cart_order)) %>% 
  plot_ly(y = ~add_to_cart_order, color = ~department, type = "box", colors = "viridis") %>% 
  layout(title = "Order (<35) in which each product was added to cart in each department")
instacart3
```
