---
title: "plotly"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```
After loading libraries, I used "Instacart" dataset to create a scatter plot, a bar chart and a box plot. 

```{r, message=FALSE, results='hide'}
data("instacart") 
janitor::clean_names(instacart)
```

###  Total number of items (< 500) ordered in each aisle

```{r, warning=FALSE, message=FALSE}
instacart1=
instacart %>%
  count(aisle) %>% 
  filter(n < 500) %>% 
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  plot_ly(
    x = ~aisle, y = ~n, type = "scatter", mode = "markers",
    color = ~aisle, alpha = 0.8) %>% 
  layout(title = "Total number of items (< 500) ordered in each aisle")
instacart1
```
I used count and filter to restrict total number of items ordered in each aisle less than 500. I used mutate to rank them from lowest to highest number of items ordered. Lastly, I used plot_ly to create the scatter plot.

### Total number of items (< 100000) ordered in each department 

```{r}
instacart2=
instacart %>%
  count(department) %>% 
  filter(n < 100000) %>% 
  mutate(department = fct_reorder(department, n)) %>% 
  plot_ly(
    x = ~department, y = ~n, color = ~department, type = "bar", colors = "viridis") %>% 
  layout(title = "Total number of items (< 100000) ordered in each department")
instacart2
```
I used count and filter to restrict total number of items ordered in each department less than 100000. I used mutate to rank them from lowest to highest number of items ordered. Lastly, I used plot_ly to create the bar chart.

### Mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered 

```{r, message=FALSE}
instacart3=
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarize(mean_hour = mean(order_hour_of_day)) %>%
  plot_ly(y = ~mean_hour, color = ~product_name, type = "box", colors = "viridis") %>% 
  layout(title = "Mean hour at which Pink Lady Apples and Coffee Ice Cream are ordered")
instacart3
```
I used filter to select Pink Lady Apples and Coffee Ice Cream. Then, I used group_by to group them by name of the product and day of the week on which the order was placed. Then, I used summarize to calculate mean hour of the day on which the order was placed. Lastly, I used plot_ly to create the box plot.
